Untitled

### 2021-03-16 analysis/chapters/paper_ana_20181122.Rmd
Figura extra con sondeos de relampago

fread(here("analysis", "data", "derived_data", "dominio_hgt.csv")) %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = guide_colorstrip(barwidth = 20,
                                               barheight = 0.8)) +
  geom_mapa() +
  geom_point(data = obs, aes(ConvertLongitude(lon), lat, 
                             color = source, shape = source), 
             size = 1, alpha = 0.8) + 
  scale_shape_manual(name = "Surface stations",  
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"), values = c(15, 17),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_color_manual(name =  "Surface stations", 
                     values = c("Sfc - Non-official" = "#00695c", 
                                "Sfc - Official" = "#FD8002"),
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"),
                     guide = guide_legend(override.aes = list(size = 2))) +
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  geom_point(data = square2, aes(lon, lat), size = 0.2, color = "#CC3311") +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        legend.margin = margin(),
        legend.box.spacing = margin(0, 0, 0, 0)) 
```

@@

p1 <- rbind(conv, aut, satwnd) %>% 
  .[usage.flag == 1 & rerr != 1.0e+10] %>% 
  .[, .(count_obs = .N), by = .(exp, lon.box, lat.box, date)] %>% 
  .[, .(obs_cycle = mean(count_obs, na.rm = TRUE)), by = .(exp, lon.box, lat.box)] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = obs_cycle), alpha = 0.8) +
  scale_fill_viridis_c(option = "E", trans = scales::log10_trans(),
                       guide = guide_colorbar(barwidth = 20)) +
  geom_mapa() +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E7 = "RAD"))) +
  labs(fill = "Mean number of\nobs per cycle") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

p2 <- rbind(conv, aut, satwnd) %>% 
  .[usage.flag == 1 & rerr != 1.0e+10] %>% 
  .[, ":="(lev.box = cut_round(pressure, breaks = seq(50, 1050, 50)))] %>% 
  .[, .(count_obs = .N), by = .(exp, lev.box, date)] %>% 
  .[, .(obs_cycle = mean(count_obs, na.rm = TRUE)), by = .(exp, lev.box)] %>% 
  ggplot(aes(exp, lev.box)) +
  geom_tile(aes(fill = obs_cycle)) +
  scale_fill_viridis_c(option = "E", trans = scales::log10_trans(),
                       guide = guide_colorbar(barheight = NULL)) +
  scale_x_discrete(labels = c("CONV", "AUT", "SATWND")) +
  scale_y_reverse() +
  labs(x = NULL, y = "Pressure level (hPa)", fill = "Mean number of\nobs per cycle") +
  theme_minimal() +
  theme(aspect.ratio = 2.5/1, plot.margin = unit(c(0, 0, 0, 0), "cm"))

@@

```{r}

>>>>

fread(here("analysis", "data", "derived_data", "dominio_hgt.csv")) %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = guide_colorstrip(barwidth = 20,
                                               barheight = 0.8)) +
  geom_mapa() +
  geom_point(data = obs, aes(ConvertLongitude(lon), lat, 
                             color = source, shape = source), 
             size = 1, alpha = 0.8) + 
  scale_shape_manual(name = "Surface stations",  
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"), values = c(15, 17),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_color_manual(name =  "Surface stations", 
                     values = c("Sfc - Non-official" = "#00695c", 
                                "Sfc - Official" = "#FD8002"),
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"),
                     guide = guide_legend(override.aes = list(size = 2))) +
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  geom_point(data = square2, aes(lon, lat), size = 0.2, color = "#CC3311") +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        legend.margin = margin(),
        legend.box.spacing = margin(0, 0, 0, 0))

lista_sondeos <- fread(here("analysis/data/derived_data/lista_sondeos.csv")) %>% 
  .[, periodo := fcase(nominal_launch_time %between% c(ymd_hms("20181121150000"), ymd_hms("20181121210000")),  "IOP07", 
                       nominal_launch_time %between% c(ymd_hms("20181122140000"), ymd_hms("20181122200000")),  "IOP08", 
                       default = "Others")
  ]

fread(here("analysis", "data", "derived_data", "dominio_hgt.csv")) %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = guide_colorstrip(barwidth = 20,
                                               barheight = 0.8)) +
  geom_mapa() +
  coord_sf(ylim = c(-35.5, -29), xlim = c(-66.5, -61.5)) +
  geom_jitter(data = lista_sondeos, aes(lon, lat, 
                                        color = periodo,
                                        shape = periodo), 
              alpha = 0.5, size = 1.5, width = 0.03, height = 0.03) +
  scale_color_brewer(palette = "Dark2",
                     guide = guide_legend(override.aes = list(size = 2,
                                                              alpha = 1))) +
  # geom_point(data = obs, aes(ConvertLongitude(lon), lat, 
  #                            color = source, shape = source), 
  #            size = 1, alpha = 0.8) + 
  # scale_shape_manual(name = "Surface stations",  
  #                    breaks = c("Sfc - Non-official", "Sfc - Official"),
  #                    labels = c("ASWS","CSWS"), values = c(15, 17),
  #                    guide = guide_legend(override.aes = list(size = 2))) +
  # scale_color_manual(name =  "Surface stations", 
  #                    values = c("Sfc - Non-official" = "#00695c", 
  #                               "Sfc - Official" = "#FD8002"),
  #                    breaks = c("Sfc - Non-official", "Sfc - Official"),
#                    labels = c("ASWS","CSWS"),
#                    guide = guide_legend(override.aes = list(size = 2))) +
# geom_point(data = square, aes(lon, lat), size = 0.2) +
  # geom_point(data = square2, aes(lon, lat), size = 0.2, color = "#CC3311") +
labs(color = NULL, shape = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        legend.margin = margin(),
        legend.box.spacing = margin(0, 0, 0, 0))
```

@@

p1 <- rbind(conv, aut, satwnd) %>% 
  .[usage.flag == 1 & rerr != 1.0e+10] %>% 
  .[, .(count_obs = .N), by = .(exp, lon.box, lat.box, date)] %>% 
  .[, .(obs_cycle = mean(count_obs, na.rm = TRUE)), by = .(exp, lon.box, lat.box)] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = obs_cycle), alpha = 0.8) +
  scale_fill_viridis_c(option = "D", trans = scales::log10_trans(),
                       guide = guide_colorbar(barwidth = 20)) +
  geom_mapa() +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E7 = "RAD"))) +
  labs(fill = "Mean number of\nobs per cycle") +
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

p2 <- rbind(conv, aut, satwnd) %>% 
  .[usage.flag == 1 & rerr != 1.0e+10] %>% 
  .[, ":="(lev.box = cut_round(pressure, breaks = seq(50, 1050, 50)))] %>% 
  .[, .(count_obs = .N), by = .(exp, lev.box, date)] %>% 
  .[, .(obs_cycle = mean(count_obs, na.rm = TRUE)), by = .(exp, lev.box)] %>% 
  ggplot(aes(exp, lev.box)) +
  geom_tile(aes(fill = obs_cycle)) +
  scale_fill_viridis_c(option = "D", trans = scales::log10_trans(),
                       guide = guide_colorbar(barheight = NULL)) +
  scale_x_discrete(labels = c("CONV", "AUT", "SATWND")) +
  scale_y_reverse() +
  labs(x = NULL, y = "Pressure level (hPa)", fill = "Mean number of\nobs per cycle") +
  theme_minimal() +
  theme(aspect.ratio = 2.5/1, plot.margin = unit(c(0, 0, 0, 0), "cm"))

@@

```{r}
files <- Sys.glob(here("analysis/data/derived_data/count_obs_E*"))

purrr::map(files, ~fread(.x)) %>% rbindlist() %>% 
  .[, porcentaje := scales::percent(proporcion, accuracy = 0.01, trim = TRUE)] %>% 
  dcast(bufr_code ~ exp, value.var = "porcentaje") %>% 
  .[order(.[,'bufr_code']), ] %>% 
  kbl(col.names = c("Obs type", "CONV", "AUT", "SATWND")) %>% 
  kable_classic_2(full_width = F)

purrr::map(files, ~fread(.x)) %>% rbindlist() %>% 
  # .[, porcentaje := scales::percent(proporcion, accuracy = 0.01, trim = TRUE)] %>% 
  dcast(bufr_code ~ exp, value.var = "N") %>% 
  .[order(.[,'bufr_code']), ] %>% 
  kbl(col.names = c("Obs type", "CONV", "AUT", "SATWND")) %>% 
  kable_classic_2(full_width = F)
```
